% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Li, Lu}

\basicInfo{
  \email{ustc.lilu630@gmail.com} \textperiodcentered\ 
  \phone{(+86) 18916915690} \textperiodcentered\ 
}
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Science and Technology of China (USTC)}}{2011 -- 2016}
\textit{PhD} in electronic science and technology. Major is 3D data reconstruction and visualization using CUDA
\datedsubsection{\textbf{University of Science and Technology of China (USTC)}}{2007 -- 2011}
\textit{B.S.} in electronic science and technology

\section{\faUsers\ Work Experience}
\datedsubsection{\textbf{Intel Asia Pacific Research and Development Co., Ltd.} Shanghai, China}{2016 -- Present}

\datedsubsection{\textbf{multiple node training deep learning framework for Theano}}{2016.6 -- 2017.6}
\role{Dsta parallel. Create a new fullconnected layer on each node}
\begin{itemize}
  \item new fullconected layer op
  \item create googlenet on 4 nodes using parallel Theano. Validate the accrurcy
\end{itemize}

\datedsubsection{\textbf{Support Ali TianChi}}{2017.7 -- 2018.3}
\role{Model startup, profile and optimization}
\begin{itemize}
  \item run workloads on 3Dunet in Caffe on KNL and profile the bottlenneck
  \item Optimization 3D convolution layer for specific input on KNL
\end{itemize}

\datedsubsection{\textbf{Autonomous driving simulatioin platform}}{2018.4 -- 2020.6}
\role{Carla is a simulator base on UnrealEngine. it can generate realsense map for autonomous driving}
\begin{itemize}
  \item build OpenDrive format map from image exported form Carla
  \item create a ros/cyber bridge to connect Carla and Apollo. Carla send Camera,lidar,location to Apollo, Apollo sends control signal back to Carla.
  \item create scenarios so that 
  \item multiple instances of autonomous driving cars in a map. they are connected by v2x
  \item profile the bottlenck of Apollo to find oppotunity to design specific SoC
\end{itemize}

\datedsubsection{\textbf{Intel uncore simulation product CoFluent}}{2020.7 -- Present}
\role{CoFluent was original owned by Swidish team, the product transformed to our team. CoFluent has a eclipse java frontend and C++ backend.}
\begin{itemize}
  \item  establish CI/CD and personal testing platform for both Windows and Linux using Jenkins
  \item As the whole simuation is signle thread, We split the model and using process level parallelism.
  \item optimization backend C++ code by Vtune
  \item create SAG LLM chatbot to CoFluent users to search doc and function usage
\end{itemize}

\datedsubsection{\textbf{Joint research with SJTU}}{2017.4 -- Present}
\role{Our team is a partner of school of Ocean and Civil engineering}
\begin{itemize}
  \item optimization HPC workloads 
  \item computer vision. Weld pool monitoring by YOLO v8, point cloud segmentation.
  \item robot. Welding Robot planning
\end{itemize}

% Reference Test
\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
An xxx optimized for xxx\cite{verma2015large}
\begin{itemize}
  \item main contribution
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == Python > C++ > Java
  \item Platform: Linux
  \item Development: Web, xxx
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
\datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://your.blog.me
  \item GitHub: https://github.com/username
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
